Supplementary materials

### 2018-02-25 publication/supp_info.Rmd
Adapt plot to tidy frames

p1 <- plant_rel_abu %>%
  inner_join(sites, by = 'site_name') %>%
  ggplot() +
  stat_density(aes(x = abu_com_rel_log, colour = locality_name),
               position = position_identity(), geom = 'line') +
  # stat_density(aes(x = abu_tot_rel_log), geom = 'line') +
  scale_color_brewer(palette = "Blues") +
  pub_theme() +
  # guides(colour = guide_legend(title = 'locality'), linetype = guide_legend(title = 'land use')) +
  labs(colour = 'locality', x = 'relative abundance')

p2 <- plant_rel_abu %>%
  inner_join(sites, by = 'site_name') %>%
  ggplot(aes(x = abu_tot)) +
  stat_density(position = position_identity(), geom = 'line') +
  scale_color_brewer(palette = "Blues") +
  pub_theme() +
  labs(x = 'abundance (floral units)')

>>>>

p1 <- plant_rel_abu %>%
  filter(scale == 'community', 
         var_trans == 'log') %>%
  inner_join(sites, by = 'site_name') %>%
  ggplot() +
  stat_density(aes(x = rab, colour = locality_name),
               position = position_identity(), geom = 'line') +
  # stat_density(aes(x = abu_tot_rel_log), geom = 'line') +
  scale_color_brewer(palette = "Blues") +
  pub_theme() +
  # guides(colour = guide_legend(title = 'locality'), linetype = guide_legend(title = 'land use')) +
  labs(colour = 'locality', x = 'relative abundance')

p2 <- plant_rel_abu %>%
  filter(scale == 'global', 
         var_trans == 'log') %>%
  distinct() %>%
  inner_join(sites, by = 'site_name') %>%
  ggplot(aes(x = abu)) +
  stat_density(position = position_identity(), geom = 'line') +
  scale_color_brewer(palette = "Blues") +
  pub_theme() +
  labs(x = 'abundance (floral units)')
